Unknown

### 2024-04-04 ms/ms.qmd
moar methods

Within the $k^{\text{th}}$ leaf, we estimated \aax{} for each light intensity by integrating the difference in \logA between the amphi and pseudohypo \agcurve{} curves over the range of \gsw{} values where the curves overlap. We used the following equation to estimate \aax{} for the $k^{\text{th}}$ leaf at light intensity $l$ in accession $m$:

@@

$$\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.$$ 
The function $f : \Theta_1 \rightarrow \Theta_2$ maps the set $\Theta_1$ indexed by leaf type (amphi or pseudohypo), leaf replicate, light intensity, and accession to set $\Theta_2$ indexed by individual \agcurve{} curve.

@@

@@

Base model (need to add indices):

$$\text{log(A)} = \beta_0 + \beta_1 \text{log}(g_\text{sw}) + \beta_2 \text{log}(g_\text{sw}) ^ 2 + \epsilon$$
Estimate \aax{} by integrating over range of \gsw{} overlap (need to add indices for accession, replicate, light intensity):

where $\text{min(log(}g_\text{sw}))$ and $\text{max(log(}g_\text{sw}))$ are the minimum and maximum values of $\text{log(}g_\text{sw})$ where amphi and pseudohypo curves overlap. \Aamphi{} is calculated from parameter estimates $\theta_\text{amphi} \in \{\beta_{0,\text{amphi}}, \beta_{1,\text{amphi}}, \beta_{2,\text{amphi}}\}$; \Ahypo{} is calculated from parameter estimates $\theta_\text{hypo} \in \{\beta_{0,\text{hypo}}, \beta_{1,\text{hypo}}, \beta_{2,\text{hypo}}\}$ for each curve.

>>>>

Within the $k^{\text{th}}$ leaf, we estimated \aax{} for each light intensity by integrating the difference in \logA between the amphi and pseudohypo \agcurve{} curves over the range of \gsw{} values where the curves overlap (from $\min(\log(g_\text{sw}))$ to $\max(\log(g_\text{sw}))$). The estimate of \aax{} for the $k^{\text{th}}$ leaf at light intensity $l$ in accession $m$ is:

@@

$$\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.$$ 
The function $f : \Theta_1 \rightarrow \Theta_2$ maps the set $\Theta_1$ indexed by leaf type (amphi or pseudohypo), leaf replicate, light intensity, and accession to set $\Theta_2$ indexed by individual \agcurve{} curve. This mapping is necessary because the random effects structure differs between models of \loggsw on \logA and that of models predicting \aax{} described in the next section.

@@

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax{} by estimating parameters in the following equation:

$$\mathrm{AA} = ... + \epsilon$$

@@
